### 2013-08-14 mil/paper.tex
minor fixes, images
fix bibliography
remove wrong statements from MIL paper.

%\newtheorem{corollary}{Corollary}
%\newtheorem{corollarya}{Corollary}
%\newtheorem{lemma}{Lemma}
%\newtheorem{theorem}{Theorem}
%\newtheorem{theorema}{Theorem}

%\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
%\newcolumntype{C}{>{\centered\arraybackslash}X}

%\newcommand{\fix}{\marginpar{FIX}} \newcommand{\new}{\marginpar{NEW}}
%\newcommand\etal{~et\,al.~}

%\aistatsauthor{Andreas M\"uller\thanks{This work was founded by the B-IT research
%school.}  \and Sven Behnke\\ {amueller@ais.uni-bonn.de},
%{behnke@cs.uni-bonn.de}} {Department of Computer Science\\
%University of Bonn\\ 53113 Bonn, Germany \\ }

@@

\section{Restricted Dependent Case}
As remarked in \Secref{assumptions}, it is not possible to bound the instance classification error
when allowing arbitrary dependencies between instances. On the other hand, the i.i.d.\ assumption of \Secref{iid}
might be to strong in a practical setting.
Therefore, we propose an assumption that is both very general and allows learning of instance classification:
We assume that each bag has a ``hidden cause'' $Z$, conditioned on which all instances are independent.
More formally, we assume
\begin{align}
    p(x_1,\dotsc,x_r)=\int_Z p(x_1)\cdot \dotsc \cdot p(x_r) dZ.
\end{align}
The intuition behind this assumption is as follows. In the classical case of drug activity prediction~\citep{dietterich1997solving}, a bag corresponds
to a molecule and each instance corresponds to a different geometric configurations. These are certainly not independent.
If one knew the ``true'' geometric characteristics of the molecule, each configuration could be derived from that.

@@

By bounding the right hand side we obtain:
\begin{theorem}\label{bound}
    Assume all instances within a bag are independent given an unobserved bag variable. If $h_0^r \geq e_B$ the instance error $e_I$ can
    be bound by
\begin{align}
    e_I \leq h_0 -  \left ( h_0^r - e_B) \right ).
\end{align}
\end{theorem}
While this bound might not be very tight -- for example if the variables are i.i.d.\ and $r$ is big, it is clear
that it is very loose compared to Theorem~\ref{iidbound} -- it is to the authors knowledge the first theorem that shows that instance-level
predictions can not be arbitrarily bad, even in a complicated dependent setting.

If we turn to the setting where bag labels are known, the bound of Theorem~\ref{bound} can be extended outside $( h_0^r > e_B)$
using the same statement for $p(y=0)$ instead of $h_0$. If there are places where both $h_0^r < e_B$ and
$p(y=0)^r < e_B$, we can use another bound, finally yielding:

\begin{theorem}\label{globalbound}
    If all instances within a bag are independent given an unobserved bag variable and the distribution of
    bag labeld $P(Y)$ is known, the instance error $e_I$ can
    be bound by
\begin{align}
    p(h_I(x)\neq y) \leq \text{min}\{ b_h, b_Y, b_g \} 
\end{align}
with
\begin{align*}
b_g &= h_0 + p(Y=0)^\frac{1}{r} - h_0^r - p(Y=0) + e_B,  \\
b_h &= h_0 - h_0^r + e_B \text{\ if } h_0^r > e_B \text{, else }\infty, \\
b_y &= p(Y=0)^\frac{1}{r} - p(Y=0) + e_B \\
&\text{\ if } p(Y=0) > e_B \text{, else }\infty. \\
\end{align*}
\end{theorem}

@@

We introduced a restricted dependent setting for multiple instance learning, in which instances inside a bag
are only independent given an unobserved variable. We showed that without any further assumptions
on the distribution of this variable, it is possible to learn instance label prediction from bag labels
in this setting. We also provided upper and lower bounds on the instance error, given known bag labels
or an estimage of the bag error.
Empirical evaluation on a synthetic dataset with known dependen structure and known instance labels
showed that the bound are non-trivial and yield insight into the behavior of instance label errors.
We hope that this work establishes a basis for further research on instance label prediction
in multiple instance learning.
\bibliographystyle{plainnat} \bibliography{paper}

@@

\begin{theorema}
    Assume all instances within a bag are independent given an unobserved bag variable. If $h_0^r \geq e_B$ the instance error $e_I$ can
    be bound by
\begin{align}
    e_I \leq h_0 -  \left ( h_0^r - e_B) \right ).
\end{align}
\begin{proof}
    Using the proof of Theorem~\ref{iidbound}, we can obtain
\begin{multline}
    p(h_I(x)\neq y| Z) \leq p(h_I(x)=0|Z) \\
    - \left ( p(h_B(x)=0|Z) - p(h_B(X)\neq Y| Z) \right ) ^ \frac{1}{r}
\end{multline}
Taking expected values with respect to $Z$ on both sides yields
\begin{align}
    e_I \leq h_0 - \mathbb{E}_Z \left ( p(h_I(x)=0|Z)^r - p(h_B(X)\neq Y| Z) \right ) ^ \frac{1}{r}
\end{align}
Since $0 \leq p(h_I(x)=0|Z)^r - p(h_B(X)\neq Y| Z) \leq 1$, the $r$-th root of this term can
be lower bounded by the identity function, resulting in
\begin{multline}
    e_I \leq h_0 - \mathbb{E}_Z \left[  p(h_I(x)=0|Z)^r \right] - e_B 
\end{multline}
The theorem follows with Jensen's inequality.
\end{proof}
\end{theorema}

\begin{theorema}
    If all instances within a bag are independent given an unobserved bag variable and the distribution of
    bag labeld $P(Y)$ is known, the instance error $e_I$ can
    be bound by
\begin{align}
    p(h_I(x)\neq y) \leq \text{min}\{ b_h, b_Y, b_g \} 
\end{align}
with
\begin{align}
b_g &= h_0 + p(Y=0)^\frac{1}{r} - h_0^r - p(Y=0) + e_B  \\
b_h &= h_0 - h_0^r + e_B \text{\ if } h_0^r > e_B \text{, else }\infty \\
b_y &= p(Y=0)^\frac{1}{r} - p(Y=0) + e_B \\
&\text{\ if } p(Y=0) > e_B \text{, else }\infty \\
\end{align}
\begin{proof}
    The bounds given by $b_h$ follows from Theorem~\ref{bound}, and $b_y$ as described in the text.
    If both  $h_0^r < e_B$ and $p(y=0)^r < e_B$, then $0 \leq ( h_0^r + p(y=0)^r - e_B) \leq 1$ and
    we can lower bound the $r$-th root as in the proof of Theorem~\ref{bound}. This yields the bound given
    by $b_g$.
\end{proof}
\end{theorema}

>>>>

@@

\section{Restricted Dependent Case}
As remarked in \Secref{assumptions}, it is not possible to bound the instance classification error
when allowing arbitrary dependencies between instances. On the other hand, the i.i.d.\ assumption of \Secref{iid}
might be too strong in a practical setting.
Therefore, we propose an assumption that is both very general and allows learning of instance classification:
We assume that each bag has a ``hidden cause'' $Z$, conditioned on which all instances are independent.
More formally, we assume
\begin{align}
    p(x_1,\dotsc,x_r)=\int_Z p(x_1)\cdot \dotsc \cdot p(x_r) dZ.
\end{align}
The intuition behind this assumption is as follows. In the classical case of drug activity prediction~\citep{dietterich1997solving}, a bag corresponds
to a molecule and each instance corresponds to a different geometric configurations. These are certainly not independent.
If one knew the ``true'' geometric characteristics of the molecule, each configuration could be derived from that.

@@

@@

We introduced a restricted dependent setting for multiple instance learning, in which instances inside a bag
are only independent given an unobserved variable. We showed that without any further assumptions
on the distribution of this variable, it is possible to learn instance label prediction from bag labels
in this setting. We also provided upper and lower bounds on the instance error, given known bag labels
or an estimage of the bag error.
Empirical evaluation on a synthetic dataset with known dependen structure and known instance labels
showed that the bound are non-trivial and yield insight into the behavior of instance label errors.
We hope that this work establishes a basis for further research on instance label prediction
in multiple instance learning.

@@
